Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Section sign

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and initial sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass.
    Section \ref{sec:final} summaries the final sample selection procedure. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see Section 4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

@@

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in Section \ref{ssec:mtotal} that most of the \mstar{} for 
            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

@@

    To convert luminosities into \mstar{}, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have only shallow color gradients. 
    We will further justify this point by measuring their median color profiles in 
    Section \ref{ssec:ell_color}.

@@

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    At the high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
    than 0.1 dex and can be as large as 0.2--0.3 dex.  
    More importantly, the differences between \mtot{} and \mcmodel{} clearly show a 
    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
    more massive galaxies.  
    This relates to the mass-dependent nature of the stellar halos of massive 
    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
    more in the next section.
    Such differences also have important implications for estimates of the stellar 
    mass function and for studies of the environment-dependence of galaxy structure. 
    These topics will be discussed in Section \ref{sec:discussion}.

@@

    Color gradients will be discussed more in Section~\ref{ssec:ell_color}. 
    In summary, our results about the mass-dependence of \mden{} profiles should not 
    be affected by the assumption of a constant \m2l{} ratio because optical color 
    gradients in our sample do not show a dependence on stellar mass.

@@

    The procedure used to derive 1-D surface brightness profile from the 
    background-corrected, contamination-masked images is already described in 
    Section~\ref{sec:ellipse} briefly. 
    In practice, the profile at very low surface brightness level is sensitive to 
    several \texttt{Ellipse} configurations.
    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    axis length between successive ellipses, and we use the median pixel value over the
    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
    times.
    We make the above choices to make the final profile less affected by any nearby
    object, and also test the differences between the profiles derived using larger
    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
    Generally speaking, the surface brightness profile is very robust against these
    changes, especially within 100 kpc. 
    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
    parameters. 
    The profile within 100 kpc is very stable, and the only noticable difference 
    is caused by the less aggressive object-mask in the very outskirt.

@@

    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
    the priors used.   
    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
    of the key parameters.

>>>>

    This paper is organized as follows. 
    \S~\ref{sec:data} presents our data and initial sample selection. 
    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    \S~\ref{sec:mstar} describes how we estimate stellar mass.
    \S~\ref{sec:final} summaries the final sample selection procedure. 
    Our main results are presented in \S~\ref{sec:result} and discussed in 
    \S~\ref{sec:discussion}. 
    \S~\ref{sec:summary} presents our summary and conclusions.

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

@@

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in \S~\ref{ssec:mtotal} that most of the \mstar{} for 
            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

@@

    To convert luminosities into \mstar{}, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have only shallow color gradients. 
    We will further justify this point by measuring their median color profiles in 
    \S~\ref{ssec:ell_color}.

@@

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    At the high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
    than 0.1 dex and can be as large as 0.2--0.3 dex.  
    More importantly, the differences between \mtot{} and \mcmodel{} clearly show a 
    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
    more massive galaxies.  
    This relates to the mass-dependent nature of the stellar halos of massive 
    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
    more in the next section.
    Such differences also have important implications for estimates of the stellar 
    mass function and for studies of the environment-dependence of galaxy structure. 
    These topics will be discussed in \S~\ref{sec:discussion}.

@@

    Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
    In summary, our results about the mass-dependence of \mden{} profiles should not 
    be affected by the assumption of a constant \m2l{} ratio because optical color 
    gradients in our sample do not show a dependence on stellar mass.

@@

    The procedure used to derive 1-D surface brightness profile from the 
    background-corrected, contamination-masked images is already described in 
    \S~\ref{sec:ellipse} briefly. 
    In practice, the profile at very low surface brightness level is sensitive to 
    several \texttt{Ellipse} configurations.
    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    axis length between successive ellipses, and we use the median pixel value over the
    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
    times.
    We make the above choices to make the final profile less affected by any nearby
    object, and also test the differences between the profiles derived using larger
    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
    Generally speaking, the surface brightness profile is very robust against these
    changes, especially within 100 kpc. 
    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
    parameters. 
    The profile within 100 kpc is very stable, and the only noticable difference 
    is caused by the less aggressive object-mask in the very outskirt.

@@

    In \S~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
    the priors used.   
    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
    of the key parameters.
